Meta-analysis

### 2019-11-01 03_Preliminary_analysis.Rmd
small query
Edits reviewed and accepted
Corrected code based on changed data

```{r echo=FALSE, message=FALSE, warning=FALSE, include= FALSE}
# Import data
PM_MB_means <- import_data()
colnames(PM_MB_means)
```

@@

# Which row spacing leads to the higher disease severity
PM_MB_means %>%
   filter(Year >= 2017) %>%
   filter(Fungicide == "control") %>%
   ggplot(aes(y = PM_final_severity, x = row_spacing, colour = Location)) +
   geom_point() +
   #  geom_smooth()+
   scale_y_continuous(limits = c(-5, 15)) +
   theme_usq()

# Which row spacing leads to the higher yeild potential
PM_MB_means %>%
   filter(Year >= 2017) %>%
   #   filter(Fungicide == "control") %>%
   ggplot(aes(
      y = as.numeric(grain_yield.t.ha.),
      x = row_spacing,
      colour = Location
   )) +
   geom_smooth(method = "gam") +
   geom_jitter(width = 0.01) +
   #   scale_y_continuous(limits = c(-5,15))+
   theme_usq()

@@

#### Effect of Fungicide 
**on proportional yield gain with respect to time of application**
First lets look at the quantiles for each fungicide irrespective of other factors.
We will focus on proportional yield gain, compared to no treatment control, as this should partially correct for some spatial and seasonal effects.  
```{r fungicide_proportion_yield}
PM_MB_means %>%
   group_by(Fungicide) %>%
   summarise(
      n = length(prop_YG),
      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
      median = median(prop_YG, na.rm = T),
      mean = mean(prop_YG, na.rm = T),
      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
   ) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain") %>%
   kable_styling(fixed_thead = T, full_width = T)

# plot table as a box plot
PM_MB_means %>%
   filter(
      Fungicide == c(
         "200 g/l  Tebuconazole + 120 g/l  Azoxystrobin" ,
         "Azoxystrobin",
         "Tebeconazole",
         "Propiconoazole"
      )
   ) %>%
   ggplot(aes(y = prop_YG, x = Fungicide)) +
   geom_boxplot() +
   geom_hline(aes(yintercept = 0), size = 0.5) +
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yield saved",
        title = "Grain yield proportion saved grouped by\nFungicide type") +
   theme(
      panel.grid.major = element_line(colour = "grey80"),
      panel.grid.minor = element_line(colour = "grey50"),
      panel.background = element_rect(fill = NA)
   ) +
   guides(fill = guide_legend(title = "Fungicide")) +
   coord_cartesian() +
   coord_flip()
#theme(axis.text.x = element_text(angle = 30, hjust =.6, vjust = 0.83))
#scale_x_continuous(limits = c(-0.3,0.6))

@@

```{r Fungicide_x_nSprays, message=FALSE}
PM_MB_means %>%
   group_by(Fungicide, total_Fungicide) %>%
   summarise(
      n = length(prop_YG),
      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
      median = median(prop_YG, na.rm = T),
      mean = mean(prop_YG, na.rm = T),
      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
   ) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain") %>%
   kable_styling(fixed_thead = T, full_width = T)

PM_MB_means %>%
   filter(total_Fungicide == 1 | total_Fungicide == 2) %>%
   filter(
      Fungicide != "Pyrazophos" &
         Fungicide != "control" &
         Fungicide != "Benomyl" &
         Fungicide != "Acibenzolar-S-Methyl" &
         Fungicide != "200g/L Azoxystrobin + 80 g/L Cyproconazole + adj"
   ) %>%
   ggplot(aes(y = prop_YG, x = Fungicide)) +
   facet_grid(rows = vars(total_Fungicide)) +
   geom_boxplot(aes(fill = Fungicide, alpha = 0.5)) +
   geom_hline(aes(yintercept = 0), size = 0.5) +
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(y = "Proportion of grain yield saved",
        title = "Grain yield proportion saved\ngrouped by Fungicide type") +
   theme_usq() +
   theme(legend.position = "none") +
   coord_cartesian() +
   scale_x_discrete(
      limits = c(
         "200 g/l  Tebuconazole + 120 g/l  Azoxystrobin",
         "Propiconazole",
         "Tebeconazole",
         "200g/L Azoxystrobin + 80 g/L Cyproconazole",
         "Sulphur",
         "Carbendazim",
         "Pyraclostrobin",
         "Azoxystrobin"
      )
   ) +
   #  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))+
   coord_flip()
#scale_x_continuous(limits = c(-0.3,0.6))

levels(PM_MB_means$Fungicide)

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE, include= FALSE}
# Import data
PM_MB_means <- import_data()
colnames(PM_MB_means)
class(PM_MB_means$year)
```

@@

# Which row spacing leads to the higher disease severity
PM_MB_means %>%
   filter(year == 2017 |
             year == 2018) %>%
   filter(fungicide == "control") %>%
   ggplot(aes(y = PM_final_severity, x = row_spacing, colour = location)) +
   geom_point() +
   #  geom_smooth()+
   scale_y_continuous(limits = c(-5, 15)) +
   theme_usq()

# Which row spacing leads to the higher yeild potential
PM_MB_means %>%
   filter(year == 2017|
             year == 2018) %>%
   #   filter(Fungicide == "control") %>%
   ggplot(aes(
      y = as.numeric(grain_yield.t.ha.),
      x = row_spacing,
      colour = location
   )) +
   geom_smooth(method = "gam") +
   geom_jitter(width = 0.01) +
   #   scale_y_continuous(limits = c(-5,15))+
   theme_usq()

@@

#### Effect of Fungicide 
**on proportional yield gain with respect to time of application**
First lets look at the quantiles for each fungicide irrespective of other factors.
We will focus on proportional yield gain, compared to no treatment control, as this should partially correct for some spatial and seasonal effects.  
```{r fungicide_proportion_yield}
PM_MB_means %>%
   group_by(fungicide) %>%
   summarise(
      n = length(prop_YG),
      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
      median = median(prop_YG, na.rm = T),
      mean = mean(prop_YG, na.rm = T),
      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
   ) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain") %>%
   kable_styling(fixed_thead = T, full_width = T)

unique(PM_MB_means$fungicide)
# plot table as a box plot
PM_MB_means %>%
   filter(
      fungicide == c(
         "200 g/L tebuconazole + 120 g/L azoxystrobin" ,
         "200 g/L azoxystrobin + 80 g/L cyproconazole",
         "tebuconazole",
         "propiconazole"
      )
   ) %>%
   ggplot(aes(y = prop_YG, x = fungicide)) +
   geom_boxplot() +
   geom_hline(aes(yintercept = 0), size = 0.5) +
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yield saved",
        title = "Grain yield proportion saved grouped by\nFungicide type") +
   theme(
      panel.grid.major = element_line(colour = "grey80"),
      panel.grid.minor = element_line(colour = "grey50"),
      panel.background = element_rect(fill = NA)
   ) +
   guides(fill = guide_legend(title = "Fungicide")) +
   coord_cartesian() +
   coord_flip()
#theme(axis.text.x = element_text(angle = 30, hjust =.6, vjust = 0.83))
#scale_x_continuous(limits = c(-0.3,0.6))

@@

```{r Fungicide_x_nSprays, message=FALSE}
PM_MB_means %>%
   group_by(fungicide, total_fungicide) %>%
   summarise(
      n = length(prop_YG),
      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
      median = median(prop_YG, na.rm = T),
      mean = mean(prop_YG, na.rm = T),
      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
   ) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain") %>%
   kable_styling(fixed_thead = T, full_width = T)

PM_MB_means %>%
   filter(total_fungicide == 1 | total_fungicide == 2) %>%
   filter(
      fungicide != "pyrazophos" &
         fungicide != "control" &
         fungicide != "benomyl" &
         fungicide != "Acibenzolar-S-methyl" &
         fungicide != "200g/L azoxystrobin + 80 g/L cyproconazole + adj"
   ) %>%
   ggplot(aes(y = prop_YG, x = fungicide)) +
   facet_grid(rows = vars(total_fungicide)) +
   geom_boxplot(aes(fill = fungicide, alpha = 0.5)) +
   geom_hline(aes(yintercept = 0), size = 0.5) +
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(y = "Proportion of grain yield saved",
        title = "Grain yield proportion saved\ngrouped by Fungicide type") +
   theme_usq() +
   theme(legend.position = "none") +
   # coord_cartesian() +
   # scale_x_discrete(
   #    limits = c(
   #       "200 g/l  Tebuconazole + 120 g/l  Azoxystrobin",
   #       "Propiconazole",
   #       "Tebeconazole",
   #       "200g/L Azoxystrobin + 80 g/L Cyproconazole",
   #       "Sulphur",
   #       "Carbendazim",
   #       "Pyraclostrobin",
   #       "Azoxystrobin"
   #    )
   # ) +
   #  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))+
   coord_flip()
#scale_x_continuous(limits = c(-0.3,0.6))
